
\section{Basic Search Algorithms and Notation}

\astar is a standard search algorithm for finding an optimal cost path from an initial state $s$ to some goal
state $s^* \in G$ in a search space represented as a graph \cite{hart1968formal}.
It expands the nodes in best-first order of $f(n)$ up to $f^*$,
where $f(n)$ is a lower bound of the cost of the shortest path that contains a node $n$ and $f^*$ is the cost of the optimal path.
The value of $f(n)$ is a sum of $g(n)$, the known shotest path cost so far from the initial node to $n$,
and $h(n)$, the heuristic lower-bound estimate of the cost from $n$ to some goal $s^*$.
% 
$h(n)$ is \emph{admissible} if it does not overestimate the true cost to
goal $h^*(n)$, which is also called a \emph{perfect heuristics}.
We omit the argument $(n)$ unless necessary.

Greedy Best First Search (GBFS) is a greedy search algorithm that finds
a satisficing solution to the problem as quickly as possible, without
explictly tries to minimize the path cost.  It expands the nodes in the
best-first order of $h(n)$, i.e. greedily guided by the
lower-bound estimate.

Both search algorithms can be described in a single style of notation, which we call \emph{sorting strategy}.
Below, we first present a general \emph{Best First Search} (BFS) algorithm template which includes  \astar, Dijkstra's algorithm \citeyear{dijkstra1959note}, Greedy Best-First Search (GBFS).
It uses two sets, OPEN and CLOSED, where unexpanded nodes are stored in OPEN and expanded nodes are stored in CLOSED. Three operations, pop$(S)$, push$(n,S)$ and remove$(n,S)$, are assumed for a node $n$ and a set $S$.
pop$(S)$ operation tries to select a single node from $S$,
push$(n,S)$ stores the node $n$ into $S$ and remove$(n,S)$ removes $n$ from $S$ if $n$ is already stored.

\begin{algorithm}                      
\begin{algorithmic}[1]
 \REQUIRE $n_0$, $\text{is\_goal}(\cdot)$, $\text{successors}(\cdot)$ %, strategy
 \STATE Initialize $\text{OPEN}=\emptyset$, $\text{CLOSED}=\emptyset$, $g(n_0)=0$, $\left(\forall n\not=n_0;\ g(n)=\infty\right)$
 % \STATE \textbf{Local procedure} $\text{open}(s,t,g_{new})$: $g(t) \leftarrow g_{new}$; $\text{parent}(t) \leftarrow s$; $\text{push}(t,\text{OPEN})$
 \STATE $\text{push}(n_0,\text{OPEN})$
 \WHILE{OPEN $\not = \emptyset$}
 \STATE $n = \text{pop}(\text{OPEN}); \text{push}(n,\text{CLOSED})$
 \RETURN $n$ \  \textbf{if} \  $\text{is\_goal}(n)=\text{true}$
 \FORALL{$m \in \text{successors}(n)$}
 \STATE $g_{new} = g(n) + \text{cost}(n,m)$
 \IF{$g_{new} < g(m)$}
 \STATE $g(m) \leftarrow g_{new}$;\; $\text{parent}(m) \leftarrow n$;\; $\text{push}(m,\text{OPEN})$;\; $\text{remove}(m,\text{CLOSED})$
 \ENDIF
 \ENDFOR
 \ENDWHILE
\end{algorithmic}
\caption{Best-First Search Algorithm using OPEN/CLOSED list}
\label{alg:ocl}
\end{algorithm}

OPEN is sorted according to a \emph{sorting strategy} and the node selected by pop$(S)$ always returns the best node according to the strategy.
Each sorting strategy is denoted as a vector of several \emph{sorting criteria}, such as
[$\text{criterion}_1$, $\text{criterion}_2$, $\ldots$,
$\text{criterion}_k$], which defines a lexicographic ordering, 
i.e., from the OPEN list, first, select a
set of nodes using $\text{criterion}_1$, and if there are still multiple
nodes remaining in the set, then break ties using $\text{criterion}_2$
and so on, until a single node is selected.  The \emph{first-level
sorting criterion} of a strategy is $\text{criterion}_1$, the
\emph{second-level sorting criterion} is $\text{criterion}_2$, and so on.\footnote{This notation corresponds to the command line option format of Fast
Downward \cite{Helmert2006}.} %demoting sentence to footnote because a statement about command line arguments of a specific planner doesn't seem appropriate in the body of the text..
%% the word frontier is no longer used in the later text.
% \emph{final frontier} is the set of open nodes with $f^*$.


Using this notation, \astar without any tie-breaking strategy can be
denoted as a BFS with $[f]$ and \astar which breaks ties according to $h$
value is denoted as $[f,h]$.
% Similarly, GBFS is denoted as $[h]$.
Unless stated otherwise, we assume the nodes are sorted in the
increasing order of the key value and a BFS always selects the smallest
key value.

However, a sorting strategy may only provide a partial ordering, 
i.e., the sorting strategy may fail to select a single node because some nodes
may share the same sorting keys.
For such cases, a BFS algorithm must
decide which node to expand by applying some \emph{default} tie-breaking
criterion $\text{criterion}_k$ which is guaranteed to return a single node, such as  \fifo (oldest node first: first-in-first-out), \lifo
(most recently inserted first: last-in-first-out) or \ro (random ordering).
For example, \astar using $h$ tie-breaking and \fifo default tie-breaking
 is denoted as $[f,h,\fifo]$.
By definition, there is only 1 node which satisfies the default criterion, so
strategies with a default criterion guarantee a total ordering among all nodes and
are able to select a single node from the set of nodes.
When the default criterion is irrelevant to the discussion,
we either use a wildcard ``*'', e.g. $[f,h,*]$, or sometimes omit it altogether for brevity.

Given a search algorithm with a sorting strategy, 
a $\plateau{\text{criterion}\ldots}$ is a set of nodes in OPEN whose elements share
the same sort keys according to non-default sorting criteria and are therefore
indistinguishable. In the case of \astar
using tie-breaking with $h$ (sorting strategy $[f,h,*]$), the plateaus are denoted as
$\plateau{f,h}$, the set of nodes with the same $f$ cost and the same $h$ cost.
We can also refer to a specific plateau with $f=f_p$ and $h=h_p$ by $\plateau{f_p,h_p}$.

An \emph{entrance} to a $\plateau{\text{criterion}\ldots}=P$ is
a node $n \in P$, whose current parent is not in
$P$. The \emph{final plateau} is the plateau
containing the solution found by the search algorithm.  In \astar using
admissible heuristics, the final plateau is $\plateau{f^*}$ (without
tie-breaking), or $\plateau{f^*,0}$ (with $h$-based tie-breaking).

Finally, OPEN list \emph{alternation}  \cite{RogerH10} is a technique to combine multiple
sorting strategies in order to improve the robustness of the search algorithm.
Nodes are simultaneously stored and sorted into
independent OPEN lists with different strategies, and
node expansion alternates among the OPEN lists.
We denote an alternating OPEN list as $\mit{alt}(X_1,X_2,\ldots)$ where
each $X_i$ is a sorting strategy.
